Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-3mm}}

@@

    \vspace{3mm}
    \figcapup 
    \caption{Result comparison on $k$-SJ problem for a constant $k$}
    \label{tab:results-com}
    \figcapdown \vspace{-5mm}
\end{table}

@@

\begin{theorem} \label{thm:main-recur}
    Equipped with the algorithm $\A$ as described above, the $k$-SJ problem with $k \ge 3$ can be solved in time
    \myeqn{
        O(k^3) \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big)
        %\nn
        \label{eqn:main:reccurrence}
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem. Furthermore, if $\A$ is comparison-based, so is the $k$-SJ algorithm.

%     time using $O(n + \out)$ space, plus the worst-case space of $\A$ on any $(k-1)$-SJ instance with input size $n$ and output size $\out$.
\end{theorem}

@@

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have 
        \myitems{
            \item $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$;
            \item $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. 
        }

        \vspace{2mm}

@@

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}

@@

\extraspacing{\em Proof of Statement (1).} We will map each $r^*$ of $\bigcup_{i = 1}^{k-2} R_i^*$ to a unique tuple $\bm{t}$ in $\J(R_1',...,R_{k-2}')$ satisfying $\dcross_H(\bm{t})$ $= \cross_H(r^*)$. After this, we can then derive
\myeqn{
    \sum_{i\in[k-2]}\sum_{r^*\in R_i^*} |\cross_H(r^*)| \leq \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}|\dcross_H(\bm{t})|\leq \out \nn
}
where the last step used  statement (3) of Lemma~\ref{lmm:hv:type1:properties}.

>>>>

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{1.5mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-3mm}}

@@

    \vspace{2mm}
    \figcapup 
    \caption{Result comparison on $k$-SJ problem for a constant $k$}
    \label{tab:results-com}
    \figcapdown \vspace{-5mm}
\end{table}

@@

\begin{theorem} \label{thm:main-recur}
    Equipped with the algorithm $\A$ as described above, the $k$-SJ problem with $k \ge 3$ can be solved in time
    \myeqn{
        O(k^3) \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big)
        %\nn
        \label{eqn:main:reccurrence}
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem. Furthermore, if $\A$ is comparison-based, so is the $k$-SJ algorithm.
\end{theorem}

@@

        \item Consider any a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_1$. Let $r'_i$ ($i \in [k-2])$ be the trimmed rectangle of $r_i$, and set $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2})$. Then, we must have (i) $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, and (ii) $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.

@@

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{1.5mm} \noindent}

@@

\extraspacing \underline{\em Proof of Statement (1).} We will map each $r^*$ of $\bigcup_{i = 1}^{k-2} R_i^*$ to a unique tuple $\bm{t}$ in $\J(R_1',...,R_{k-2}')$ satisfying $\dcross_H(\bm{t})$ $= \cross_H(r^*)$. After this, we can then derive
\myeqn{
    \sum_{i\in[k-2]}\sum_{r^*\in R_i^*} |\cross_H(r^*)| \leq \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}|\dcross_H(\bm{t})|\leq \out \nn
}
where the last step used  statement (3) of Lemma~\ref{lmm:hv:type1:properties}.
